Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-09-15 WSSSPE3/report/WSSSPE3_review.tex
a few more changes to explain the restructured paper

>>>>

This section captures detailed reports from each working group that made significant
progress.  Each subsection records the discussion of
a group, as written by that group at that time (in the first person and in the present\slash future tense.)
Thus, the subsections are records of what the groups did and planned, as of the end of the WSSSPE3 workshop.
